\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2023-03-27 Latex/paper-resum.tex
# last version with correction in appendix

\begin{theorem}\label{Th_CA_futures}[Convexity Adjustment approximation for Futures]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for futures is 
\begin{equation}\label{ca_approximation_futures}
CA(t,t_0,t_1) \approx \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1) \right) \int_{0}^{t_0} \beta(s,t_0,x_0,\hat{y}_s) \nu(s,t_2) ds. 
\end{equation}
with 
\begin{equation*}
\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x,y).
\end{equation*}
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_futures}.
\end{proof}

@@

\begin{lemma}\label{DsX}[Approximation $D_s \bar{x}_{t_a}$]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, 
\begin{equation}\label{approximation_D_s_x_t}
D_s \bar{x}_{t_a} = \beta(s,t_a,\bar{x}_s,\bar{y}_s) \bar{M}(s,t_a)
where
\bar{M}(s,t_a) &= \exp\left(-\int_{s}^{t_a} \left( \frac{\left(\partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a})\right)^{2}}{2} - \exp\left(-\int_{u}^{t_a}k_u du\right) \partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,t_p))\right) du \right) \\ 
&\cdot\exp\left(\int_{s}^{t_0} \partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a}) dW^{\mathbb{Q}}_u \right)
With $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) \partial_x \eta(u,x,y)$. Then, we have that
\begin{align}\label{approsimation_E_s_x_t}
\mathbb{E}_s^{t_p}\left(D_s \bar{x}_{t_a}\right) &\approx \beta(s,t_a,\bar{x}_s,\bar{y}_s) \bar{DM}(s,t_a).
where 
\bar{DM}(s,t_a) &= \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\left(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) \right. \right. \right. \\
&+ \left. \left. \left. \eta(u,\bar{x}_0(t_a), \bar{y}_{u})) \partial_x \bar{\nu}(t,t_p, \bar{x}_0(t_a)) du \right) \right)\right) 
\end{lemma}
\begin{proof}
Using the relation 
dW^{\mathbb{Q}^{t_p}} = dW^{\mathbb{Q}} + \bar{\nu}(t,t_p) dt
where $\bar{\nu}(t,t_p) = \int_{t}^{t_p} \eta(s,\bar{x}_s,\bar{y}_s) ds$. We must observe, that we can approximate $x_s$ by 
\mathbb{E}^{t_p}(x_s) = \bar{x}_0(t_a) + \mathcal{O}\left(\int_{0}^{s}\exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) du \right)
$$. Let define
\bar{\nu}(t,t_p, \bar{x}_0(t_a))&:= \int_{t}^{t_p} \eta(s,\bar{x}_0(t_a),\bar{y}_s) ds\\
\partial_x \bar{\nu}(t,t_p, \bar{x}_0(t_a))&:= \int_{t}^{t_p} \partial_x \eta(s,\bar{x}_0(t_a),\bar{y}_s) ds\\
Then, we have that under the measure $\mathbb{Q}^{t_p}$ 
\bar{x}_{t_a} = \bar{x}_0(t_a) &+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_s ds - \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{\nu}(s, t_p) \eta(s,\bar{x}_s,\bar{y}_s) ds   \\
&+ \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right)\eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}^{t_p}}. 
Now, if we apply $D_s$ in above equality and we use the last approximation we have that
\mathbb{E}_s(D_s \bar{x}_{t_a}) &\approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right)\\ &\cdot \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\left(\partial_x (\eta(u, \bar{x}_0(t_a), \bar{y}_{u})) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) \right. \right. \right. \\
&+ \left. \left. \left. \eta(u, \bar{x}_0(t_a), \bar{y}_{u})) \partial_x  \bar{\nu}(t,t_p, \bar{x}_0(t_a)) du \right)\right)\right) 
\end{proof}

@@

The reason of $\epsilon^{2}$ in $y_{\epsilon,t}$ is because $\mathbb{E}\left(y_t\right)= \mathbb{V}ar(x_t)$. Then, if the scale of $x_{\epsilon,t}$ is $\epsilon$ then the scale of $y_{\epsilon,t}$ must be $\epsilon^{2}$. We will start with the estimation of $\mathbb{E}((y_t - \bar{y}_t)^{2})$. We will define the next parametrization for $\nu in [0,1]$

@@

\eta^{2}(u, x_u, y_u) &= \eta^{2}(u, 0, 0) + \int_{0}^{1} \partial_{\nu}z^{nu}_{u} d\nu \\ 

@@

\mathbb{E}((E_{y}(t))^{2}) &\leq 4 \mathbb{E}\left(\int_{0}^{t} \exp\left(-4 \int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \left(\int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \|\nabla_{x,y}\eta(u, \nu x_u, \nu y_u)\|^{2} \|(x_u, y_u)\| d\nu \right)^2 du \right) ^{2}\nonumber \\ 
&\leq 4 \|\eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\partial_y\|\eta\|^{2}_{\infty} ) \int_{0}^{t} \mathbb{E}\left( \|(x_u, y_u)\|^{2}\right) du = M^{y}_k \int_{0}^{t} \mathbb{E}\left( \|(x_u, y_u)\|^{2}\right) du

@@

The next step is to estimate $\mathbb{E}((x_t - \bar{x}_t)^{2})$. From the definition of $x_t$, we have that

@@

x_t = \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \bar{y}_u du + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E{y}(u) du + \int_{0}^{t} \eta(t,x_u,y_u) dW_u. 

@@

 \mathbb{E}((E_x(u))^{2}) \leq \|\partial_y \eta \|^{2}_{\infty} \mathbb{E}((E_{y}(u))^{2})   

@@

Tne using \ref{upper_bound_E_y} we get that

@@

 \mathbb{E}((E_x(u))^{2}) \leq 4 \|\eta\|^{2}_{\infty} \|\partial_y \eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\partial_y\|\eta\|^{2}_{\infty} ) \int_{0}^{u} \mathbb{E}\left( \|(x_s, y_s)\|^{2}\right) ds

@@

\mathbb{E}((x_t - \bar{x}_t)^{2}) & \leq 2 \mathbb{E}\left( \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}(u) du    \right)^2 + \mathbb{E}\left( \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{x}(u) dW_u\right)^{2} \\
&\leq 2 \mathbb{E}\int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}(E^{2}_{y}(u)) du + \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}(E^{2}_{x}(u)) du   

@@

\mathbb{E}((x_t - \bar{x}_t)^{2}) \leq M^{x}_k \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}\left( \|(x_u, y_u)\|^{2}\right) du 

@@

To end, only we have to estimate $\mathbb{E}\left( \|(x_s, y_s)\|^{2}\right)$. We will start with $\mathbb{E}(y^{2}_u)$.From the definition of $y_t$ and since $\|\eta\|_{\infty} < \infty$, we have that

@@

\mathbb{E}(y^{2}_u) \leq \|\eta\|^{2}_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds.

@@

\lim_{t \to 0} \mathbb{E}(y^{2}_u) = \|\eta\|^{2}_{\infty} t

@@

\lim_{t \to \infty} \mathbb{E}(y^{2}_u) < \infty.

@@

Now $\mathbb{E}(x^{2}_u)$. From the definition of $x_t$ and using $(a+b)^2 \leq 2(a^{2}+ b^{2})$ we have that

@@

\mathbb{E}(x^{2}_u) &\leq 2 \mathbb{E}\left(\int_{0}^{u} \exp\left(- \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) y_s  ds \right)^{2} +  2 \mathbb{E}\left(\int_{0}^{u} \exp\left(- \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \eta(s,x_s,y_s)  dW_s \right)^{2} \nonumber \\
&\leq 2 \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \mathbb{E}\left(y_s\right)^{2} ds + 2 \int_{0}^{u} \exp\left(- 2 \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \mathbb{E}\left(\eta^{2}(s,x_s,y_s)\right) ds \\

@@

\lim_{t \to 0} \mathbb{E}(x^{2}_u) = 2\|\eta\|^{2}_{\infty} t

@@

and when ($u \to \infty$) we have that $\mathbb{E}(x^{2}_u)$ remains bounded. Then, if we use the above inequalities 

@@

\mathbb{E}((y_t - \bar{y}_t)^{2}) &\leq M^{y}_k \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds du

@@

\mathbb{E}((x_t - \bar{x}_t)^{2}) &\leq 2 M^{x}_k \|\eta\|_{\infty} \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)   \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \int_{0}^{s}  \exp\left(- 2\int_{s_1}^{s} k(u^{\prime}) du^{\prime}\right) ds_1 ds du \\
&+ (2 M^{x}_K \|\eta\|_{\infty} + 1) \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds du

@@

\subsection{Approximation of $\mathbb{E}_s^{\mathbb{Q}}\left(D_s \bar{x}_{t_a}\right)$}
As above appendix we have that
\begin{align*}
\bar{x}_{t_a} &= \bar{x}_0(t_a) + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{\mathbb{Q}}\\
\end{align*}
and therefore (see (\ref{approsimation_E_s_x_t}))
\begin{equation}
D_s \bar{x}_{t_a} =  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_s,\bar{y}_{s})\bar{M}(s,t_a)
\end{equation}
Now, if we take $\mathbb{E}^{\mathbb{Q}}\left(\cdot\right)$ we get
\begin{equation}\label{approximation_spot_E_s_x_t}
\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right)=\exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_s,\bar{y}_{s})
\end{equation}
Therefore, we have that
\begin{equation}\label{approximation_spot_E_s_x_t}
\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right)= \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0(t_a),\bar{y}_{s}) + E(s)
\end{equation}
where $\mathbb{E}(E^{2}(s)) \sim \mathcal{O}(s)$ when $s \to 0$.

>>>>

\begin{theorem}\label{Th_CA_futures}[Convexity Adjustment approximation for Futures]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for futures is 
\begin{equation}\label{ca_approximation_futures}
CA(t,t_0,t_1) \approx \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1) \right) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds. 
\end{equation}
with 
\begin{equation*}
\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{t_0}k_u du \right) \eta(u,x,y).
\end{equation*}
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_futures}.
\end{proof}

@@

@@

The reason of $\epsilon^{2}$ in $y_{\epsilon,t}$ is because $\mathbb{E}^{\mathbb{Q}}\left(y_t\right)= \mathbb{V}ar(x_t)$. Then, if the scale of $x_{\epsilon,t}$ is $\epsilon$ then the scale of $y_{\epsilon,t}$ must be $\epsilon^{2}$. We will start with the estimation of $\mathbb{E}^{\mathbb{Q}}((y_t - \bar{y}_t)^{2})$. We will define the next parametrization for $\nu \in [0,1]$

@@

\eta^{2}(u, x_u, y_u) &= \eta^{2}(u, 0, 0) + \int_{0}^{1} \partial_{\nu}z^{\nu}_{u} d\nu \\ 

@@

\mathbb{E}^{\mathbb{Q}}((E_{y}(t))^{2}) &\leq 4 \mathbb{E}^{\mathbb{Q}}\left(\int_{0}^{t} \exp\left(-4 \int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \left(\int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \|\nabla_{x,y}\eta(u, \nu x_u, \nu y_u)\|^{2} \|(x_u, y_u)\| d\nu \right)^2 du \right) ^{2}\nonumber \\ 
&\leq 4 \|\eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\|\partial_y \eta\|^{2}_{\infty} ) \int_{0}^{t} \mathbb{E}^{\mathbb{Q}}\left( \|(x_u, y_u)\|^{2}\right) du = M^{y}_k \int_{0}^{t} \mathbb{E}^{\mathbb{Q}}\left( \|(x_u, y_u)\|^{2}\right) du

@@

The next step is to estimate $\mathbb{E}^{\mathbb{Q}}((x_t - \bar{x}_t)^{2})$. From the definition of $x_t$, we have that

@@

x_t = \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \bar{y}_u du + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}(u) du + \int_{0}^{t} \eta(t,x_u,y_u) dW_u. 

@@

 \mathbb{E}^{\mathbb{Q}}((E_x(u))^{2}) \leq \|\partial_y \eta \|^{2}_{\infty} \mathbb{E}^{\mathbb{Q}}((E_{y}(u))^{2})   

@@

Then using (\ref{upper_bound_E_y}) we get that

@@

 \mathbb{E}^{\mathbb{Q}}((E_x(u))^{2}) \leq 4 \|\eta\|^{2}_{\infty} \|\partial_y \eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\|\partial_y \eta\|^{2}_{\infty} ) \int_{0}^{u} \mathbb{E}^{\mathbb{Q}}\left( \|(x_s, y_s)\|^{2}\right) ds

@@

\mathbb{E}^{\mathbb{Q}}((x_t - \bar{x}_t)^{2}) & \leq 2 \mathbb{E}^{\mathbb{Q}}\left( \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}(u) du    \right)^2 + \mathbb{E}^{\mathbb{Q}}\left( \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{x}(u) dW_u\right)^{2} \\
&\leq 2 \mathbb{E}^{\mathbb{Q}}\int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}(E^{2}_{y}(u)) du + \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}(E^{2}_{x}(u)) du   

@@

\mathbb{E}^{\mathbb{Q}}((x_t - \bar{x}_t)^{2}) \leq M^{x}_k \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}\left( \|(x_u, y_u)\|^{2}\right) du 

@@

To end, only we have to estimate $\mathbb{E}^{\mathbb{Q}}\left( \|(x_s, y_s)\|^{2}\right)$. From the definition of $y_t$ and since $\|\eta\|_{\infty} < \infty$, we have that

@@

\mathbb{E}^{\mathbb{Q}}(y^{2}_u) \leq \|\eta\|^{2}_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds.

@@

\lim_{t \to 0} \mathbb{E}^{\mathbb{Q}}(y^{2}_u) = \|\eta\|^{2}_{\infty} t

@@

\lim_{t \to \infty} \mathbb{E}^{\mathbb{Q}}(y^{2}_u) < \infty.

@@

Now $\mathbb{E}^{\mathbb{Q}}(x^{2}_u)$. From the definition of $x_t$ and using $(a+b)^2 \leq 2(a^{2}+ b^{2})$ we have that

@@

\mathbb{E}^{\mathbb{Q}}(x^{2}_u) &\leq 2 \mathbb{E}^{\mathbb{Q}}\left(\int_{0}^{u} \exp\left(- \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) y_s  ds \right)^{2} +  2 \mathbb{E}^{\mathbb{Q}}\left(\int_{0}^{u} \exp\left(- \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \eta(s,x_s,y_s)  dW_s \right)^{2} \nonumber \\
&\leq 2 \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}\left(y_s\right)^{2} ds + 2 \int_{0}^{u} \exp\left(- 2 \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}\left(\eta^{2}(s,x_s,y_s)\right) ds \\

@@

\lim_{t \to 0} \mathbb{E}^{\mathbb{Q}}(x^{2}_u) = 2\|\eta\|^{2}_{\infty} t

@@

and when ($u \to \infty$) we have that $\mathbb{E}^{\mathbb{Q}}(x^{2}_u)$ remains bounded. Then, if we use the above inequalities 

@@

\mathbb{E}^{\mathbb{Q}}((y_t - \bar{y}_t)^{2}) &\leq M^{y}_k \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds du

@@

\mathbb{E}^{\mathbb{Q}}((x_t - \bar{x}_t)^{2}) &\leq 2 M^{x}_k \|\eta\|_{\infty} \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)   \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \int_{0}^{s}  \exp\left(- 2\int_{s_1}^{s} k(u^{\prime}) du^{\prime}\right) ds_1 ds du \\
&+ (2 M^{x}_K \|\eta\|_{\infty} + 1) \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds du.

@@

Therefore, we have that
\mathbb{E}^{\mathbb{Q}}((x_t - \bar{x}_t)^{2}) &\leq \frac{2}{3} M^{x}_k \|\eta\|_{\infty} \left( \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) \right) du  \right)^{3}  \\
&+ \frac{(2 M^{x}_K \|\eta\|_{\infty} + 1)}{2} \left( \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) \right) du  \right)^{2}.

\begin{lemma}\label{DsX}[Approximation $D_s \bar{x}_{t_a}$]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, 
\begin{align}\label{approximation_D_s_x_t}
D_s \bar{x}_{t_a} &= \beta(s,t_a,\bar{x}_s,\bar{y}_s) \bar{M}(s,t_a,t_p) \quad \text{under the measure $\mathbb{Q}^{t_p}$} \nonumber \\
D_s \bar{x}_{t_a} &= \beta(s,t_a,\bar{x}_s,\bar{y}_s) \bar{M}(s,t_a)  \quad \text{under the measure $\mathbb{Q}$}
\end{align}
where
\begin{align*}
\bar{M}(s,t_a,t_p) &= \exp\left(-\int_{s}^{t_a} \left( \frac{\left(\partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a})\right)^{2}}{2} - \exp\left(-\int_{u}^{t_a}k_u du\right) \partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,t_p))\right) du \right) \\ 
&\cdot\exp\left(\int_{s}^{t_0} \partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a}) dW^{\mathbb{Q}}_u \right)
\end{align*}
and
\begin{equation*}
\bar{M}(s,t_a) = \exp\left(-\int_{s}^{t_a} \left( \frac{\left(\partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a})\right)^{2}}{2} - \right) du \right) \exp\left(\int_{s}^{t_0} \partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a}) dW^{\mathbb{Q}}_u \right)
\end{equation*} 
With $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) \partial_x \eta(u,x,y)$. We have also that
\begin{align}\label{approsimation_E_s_x_t}
\mathbb{E}_s^{t_p}\left(D_s \bar{x}_{t_a}\right) &\approx \beta(s,t_a,\bar{x}_s,\bar{y}_s) \bar{DM}(s,t_a) \nonumber \\
\mathbb{E}_s^{\mathbb{Q}}\left(D_s \bar{x}_{t_a}\right)&\approx \beta(s,t_a,\bar{x}_s,\bar{y}_s)
\end{align}
where 
\begin{align*}
\bar{DM}(s,t_a) &= \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\left(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) \right. \right. \right. \\
&+ \left. \left. \left. \eta(u,\bar{x}_0(t_a), \bar{y}_{u})) \partial_x \bar{\nu}(t,t_p, \bar{x}_0(t_a)) \right)  du \right)\right) 
\end{align*}
with  
\begin{align*}
\bar{\nu}(t,t_p) &= \int_{t}^{t_p} \eta(s,\bar{x}_s,\bar{y}_s) ds \\
\bar{\nu}(t,t_p, x_0) &= \int_{t}^{t_p} \eta(s,x,\bar{y}_s) ds \\
\partial_x \bar{\nu}(t,t_p,x_0) &= \int_{t}^{t_p} \eta(s,x_0,\bar{y}_s) ds\\
\end{align*}
\end{lemma}
\begin{proof}
From 
\begin{equation*}
dW^{\mathbb{Q}^{t_p}} = dW^{\mathbb{Q}} + \bar{\nu}(t,t_p) dt
\end{equation*}
we have that under the measure $\mathbb{Q}^{t_p}$ 
\begin{align*}
\bar{x}_{t_a} = \bar{x}_0(t_a) &+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_s ds - \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{\nu}(s, t_p) \eta(s,\bar{x}_s,\bar{y}_s) ds   \\
&+ \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right)\eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}^{t_p}}. 
\end{align*}
Now, if we apply $D_s$ in above equality and we use the last approximation we have that
\begin{align*}
\mathbb{E}^{t_p}_s(D_s \bar{x}_{t_a}) &\approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right)\\ &\cdot \exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\left(\partial_x (\eta(u, \bar{x}_0(t_a), \bar{y}_{u})) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) \right. \right.  \\
&+  \left. \left. \eta(u, \bar{x}_0(t_a), \bar{y}_{u})) \partial_x  \bar{\nu}(t,t_p, \bar{x}_0(t_a)) du \right)\right)
\end{align*}
\end{proof}

\subsection{Approximation of $\mathbb{E}_s^{\mathbb{Q}}\left(D_s \bar{x}_{t_a}\right)$}
As above appendix we have that
\begin{align*}
\bar{x}_{t_a} &= \bar{x}_0(t_a) + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{\mathbb{Q}}\\
\end{align*}
and therefore (see (\ref{approsimation_E_s_x_t}))
\begin{equation}
D_s \bar{x}_{t_a} =  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_s,\bar{y}_{s})\bar{M}(s,t_a)
\end{equation}
Now, if we take $\mathbb{E}^{\mathbb{Q}}\left(\cdot\right)$ we get
\begin{equation}\label{approximation_spot_E_s_x_t}
\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right)=\exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_s,\bar{y}_{s})
\end{equation}
Therefore, we have that
\begin{equation}\label{approximation_spot_E_s_x_t}
\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right)= \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0(t_a),\bar{y}_{s}) + E(s)
\end{equation}
where $\mathbb{E}^{\mathbb{Q}}(E^{2}(s)) \sim \mathcal{O}(s)$ when $s \to 0$.
